\documentclass[12pt]{article}
\usepackage[a4paper,landscape,margin=1in]{geometry}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\begin{document}
\begin{flushleft}
{\Huge\textbf{Slide 1. Slide 1. Why Lubelskie}}
\vspace{6mm}\par
\rule{0.96\textwidth}{0.4pt}\vspace{6mm}\par
\begin{itemize}
\item Lubelskie is an EU Less Developed region (NUTS-2 PL81), with structural regional gap and lower income base than the EU and Poland average.
\item It is exposed to border-region pressures, demographic aging, and public-service gaps.
\item The same intervention is needed to tackle: regional inequality, climate-transition risk, and social fairness.
\end{itemize}
\end{flushleft}
\newpage
\begin{flushleft}
{\Huge\textbf{Slide 2. Slide 2. Why the Proposal Is Credible}}
\vspace{6mm}\par
\rule{0.96\textwidth}{0.4pt}\vspace{6mm}\par
\begin{itemize}
\item The assignment asks for ERDF and JTF together; we frame this as a two-window, one strategy.
\item Current baseline: ERDF is available for Lubelskie; JTF is currently constrained and assumed to be open in the next period.
\item Therefore: use the 2028–2034 cycle as the implementation scenario, with ERDF-ready preparation in advance.
\end{itemize}
\end{flushleft}
\newpage
\begin{flushleft}
{\Huge\textbf{Slide 3. Slide 3. Stage 1: ERDF Package (Foundation)}}
\vspace{6mm}\par
\rule{0.96\textwidth}{0.4pt}\vspace{6mm}\par
\begin{itemize}
\item Focus: clean public infrastructure and small/medium enterprise transition capacity.
\item Core actions: energy-efficient municipal buildings, low-emission local mobility, and SME energy upgrades.
\item Direct outcomes by 2029: lower energy costs, stronger local job capacity, faster project execution readiness.
\end{itemize}
\end{flushleft}
\newpage
\begin{flushleft}
{\Huge\textbf{Slide 4. Slide 4. Stage 2: JTF Layer (Transition Support)}}
\vspace{6mm}\par
\rule{0.96\textwidth}{0.4pt}\vspace{6mm}\par
\begin{itemize}
\item Focus: workers and communities most exposed to green transition.
\item Core actions: re-training with job matching, conversion support for vulnerable local supply chains, and brownfield repurposing.
\item Direct outcomes by 2034: lower social stress from transition, reduced regional lock-in, stable transition governance.
\end{itemize}
\end{flushleft}
\newpage
\begin{flushleft}
{\Huge\textbf{Slide 5. Slide 5. One Program, Two Funds, One Logic}}
\vspace{6mm}\par
\rule{0.96\textwidth}{0.4pt}\vspace{6mm}\par
\begin{itemize}
\item ERDF and JTF do not replace each other; they are sequenced in the same regional contract.
\item No double financing: stage-specific costs, stage-specific beneficiaries, shared monitoring indicators.
\item Decision point for EU: one package that reduces inequality now and reduces transition damage later.
\end{itemize}
\end{flushleft}
\end{document}